\noindent\textbf{Main problem:}
The main problem is to create a working application, based on modular design, to recognise human emotions through facial- and speech-expressions. \\


\noindent The problem will be addressed by answering the following research questions:
\begin{enumerate}

\item To which extent can emotions be recognised through the applied models? 

\item What modules are required for the application? 

\item What is necessary to combine different approaches?

\end{enumerate}

\noindent It is important to know to what extent the model can accurately predict outcomes to make the application as accurate as possible, however, a good-enough classification accuracy will be accepted as the project is time constrained.

\noindent The application is to incorporate many different mechanisms and  it is crucial to know what modules needs to be created for both approaches.

\noindent To achieve a working application by combining the approaches a general application will be incorporated by using modular design choices.
\\
\noindent Some demarcations to be aware of. A problem with user feedback is that it relies on the user to not be malicious. Because of this, the evaluation of the feedback mechanism will be done in a closed environment by the project group to ensure that all feedback is benign.

\noindent The \acrlong{gui} used to implement feedback will be limited and only functional since the project is limited by time.


\noindent When creating the models, known \acrshort{cnn} will be used by implementing them in Python. \\


\noindent The research questions will be verified as follows:

\begin{enumerate}

    \item The model will produce an accuracy of the classified emotions as a percentage. A satisfactory goal  for separate emotions would be 60\%, and for grouped emotions, 80\%. The percentages are set as a guess estimate, based on previous research.\cite{pramerdorfer2016facial}
    \item To create a viable and modular solution, it is necessary to identify which modules that are needed for each approach. Simply put, if a module is created it is necessary.
    \item To combine different approaches, they must be integrated together. The identifications of these steps are crucial to make the model modular for approaches other than the ones studied here. 
\end{enumerate}
